### 2023-01-11 Manuscript/Draft1.Rmd
Updates

# Create table to present the data]
 kable(summary_tab, "simple",
                     caption = "Each index estimate chooses one condition from each of the following
225 columns. There are 3∗3∗2∗2∗2∗2∗2 = 288 VAST model combinations and 3∗3∗2∗2∗2 = 144
226 stratified mean estimates.",
          format = "latex", booktabs = TRUE) %>%
          kable_styling(latex_options = "scale_down")
```

>>>>

# Create table to present the data]
 kable(summary_tab, "simple",
                     caption = "Each index estimate chooses one condition from each of the following
7 columns. There are 3∗3∗2∗2∗2∗2∗2 = 288 VAST model combinations and 3∗3∗2∗2∗2∗2 = 144 stratified mean estimates.",
          format = "latex", booktabs = TRUE) %>%
          kable_styling(latex_options = "scale_down")
```

### 2023-01-11 Manuscript/Draft1.tex
Updates

\caption{\label{tab:scenarios}Each index estimate chooses one condition from each of the following
225 columns. There are 3*3*2*2*2*2*2 = 288 VAST model combinations and 3*3*2*2*2 = 144
226 stratified mean estimates.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllllll}
\toprule
Species & Population Trend & Temperature Scenario & Strata Included & Noise Added & Covariates (VAST) & Season\\
\midrule
Yellowtail & Increasing & Repeating & All strata & No & Spring & \\
Cod & Constant & Increasing 5°C & Subset & Yes & Fall & \\
Haddock & Decreasing &  &  &  &  & \\
\bottomrule
\end{tabular}}
\end{table}

>>>>

\caption{\label{tab:scenarios}Each index estimate chooses one condition from each of the following
7 columns. There are 3*3*2*2*2*2*2 = 288 VAST model combinations and 3*3*2*2*2*2 = 144 stratified mean estimates.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllllll}
\toprule
Species & Population Trend & Temperature Scenario & Strata Included & Noise Added & Season & Covariates (VAST)\\
\midrule
Yellowtail & Increasing & Repeating & All strata & No & Spring & No\\
Cod & Constant & Increasing 5°C & Subset & Yes & Fall & Yes\\
Haddock & Decreasing &  &  &  &  & \\
\bottomrule
\end{tabular}}
\end{table}
